### 2021-06-06 treatise-pdflatex/4_simulation.tex
Copy selected figures for article

We can apply DS more than once to better estimate the nonzero components;
let us call it the successive estimation \cite [CaT07].
We apply DS for the first time, and we extract largest components of the estimated vector.
Then we apply DS again, and we extract largest components of the second estimated vector.
Finally, we apply Moore–Penrose inverse to get the returned solution.
The resulting indices set has to be scrambled back according to the original indices.

@@

However, one must keep in mind that for OMP, in Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix.
Since we have here a low-complexity, random generation of beamforming matrices, a different design of sensing matrix may affect the performance of OMP.

@@

For performance metric, we follow Lee, Gil, and Lee \cite [LGL16] to use
\DispNum {h:h:lo:vg} {
\tilde {\chi}
=\RB {
   \frac {\log_2 {\VNm {\V {h} -\hat {\V {h}}} _2}}
   {\log_2 {\VNm {\V {h}}_2}}
} _{\mathsf {avg}}, 
}
However, we remark that when \m {\VNm {\V {h}}_2} is small, this can blow up.
Indeed, since we did not consider a definite a channel model in this treatise, \m {\T {\chi}} may not necessarily be proportional to the channel capacity.

>>>>

We can apply DS more than once to better estimate the nonzero components;
let us call it the successive estimation \cite {CaT07}.
We apply DS for the first time, and we extract largest components of the estimated vector.
Then we apply DS again, and we extract largest components of the second estimated vector.
Finally, we apply Moore–Penrose inverse to get the returned solution.
The resulting indices set has to be scrambled back according to the original indices.

@@

However, one must keep in mind that for OMP, in Lee, Gil, and Lee \cite {LGL16}, a high-complexity nonconvex program is used to design the sensing matrix.
Since we have here a low-complexity, random generation of beamforming matrices, a different design of sensing matrix may affect the performance of OMP.

@@

For performance metric, we follow Lee, Gil, and Lee \cite {LGL16} to use
\DispNum {h:h:lo:vg} {
\tilde {\chi}
=\RB {
   \frac {\log_2 {\VNm {\V {h} -\hat {\V {h}}} _2}}
   {\log_2 {\VNm {\V {h}}_2}}
} _{\mathsf {avg}}, 
}
However, we remark that when \m {\VNm {\V {h}}_2} is small, this can blow up.
Indeed, since we did not consider a definite a channel model in this treatise, \m {\T {\chi}} may not necessarily be proportional to the channel capacity.
